ZPY: Open Source Synthetic Data for Computer Vision

### 2021-06-24 docs/paper/paper.tex
reference cleanup, more progress

\author{
	{\hspace{1mm}Hugo Ponte}\thanks{correspondence author} \\ 
	Zumo Labs \\
	\texttt{hugo@zumolabs.ai} \\
	\And
	{\hspace{1mm}Norman Ponte} \\
	Zumo Labs \\
	\texttt{norman@zumolabs.ai} \\
	\And
	{\hspace{1mm}Sammie Crowder} \\
	Zumo Labs \\
	\texttt{sammie@zumolabs.ai} \\
	\And
	{\hspace{1mm}Kory Stiger} \\
	Zumo Labs \\
	\texttt{kory@zumolabs.ai} \\
	\And
	{\hspace{1mm}Steven Pecht} \\
	Zumo Labs \\
	\texttt{steven@zumolabs.ai} \\
	\And
	{\hspace{1mm}Michael Stewart} \\
	Zumo Labs \\
	\texttt{michael@zumolabs.ai} \\
	\And
	{\hspace{1mm}Elena Ponte} \\
	Zumo Labs \\
	\texttt{elena@zumolabs.ai} \\
}

@@

Deep learning has exploded in popularity due to large open source frameworks such as tensorflow and pytorch
What is synthetic data (references)

@@

@@

In addition to supporting the full breadth of the 3D workflow, Blender has the unique strength of using Python as the programming language of choice for asset scripting. Python has emerged as the lingua franca for modern deep learning, in part due to the popularity of open-source frameworks such as TensorFlow \citep{tensorflow}, PyTorch \citep{pytorch}, and Scikit-Learn \citep{scikit-learn}. Successful adoption of synthetic data will require Machine Learning Engineers to perform asset scripting, and these engineers will be much more comfortable in Blender’s Python environment than Unity’s C# or Unreal Engine’s C++ tools.

\subsection{Synthetic Data}
\label{sec:syntheticdata}

BlenderProc, Synthesis, LexSet

@@

Given

@@

@@

\section{Design}
\label{sec:design}

@@

Pythonic syntax

@@

Extensibility

@@

The first step in the syntehtic data workflow is to design and create the \emph{sim}, short for simulation. A sim is a collection of 3D assets controlled at runtime through a single script called the \emph{run script}. The run script defines a function \lstinline{run(*)}, which acts as the point of entry for any generation process. Important parameters that configure the behavior of the run script are defined as kwargs, short for keyword arguments, in the \lstinline{run(*)} function. These kwargs allow configuration of the simulation through gin-config, a python package for configuration of python libraries \citep{ginconfig}.

@@

\begin{lstlisting}[language=Python,caption={Basic structure of a run script.},label={lst:setuploop}]
def run\left(  
	kwarg_1 : bool = False,
\right)):
	# Setup Code
	for frame in zpy.blender.step():
		# Loop Code
\end{lstlisting}

@@

Machine learning models are trained on a dataset for some time, and periodically evaluated on validation and test datasets. Model performance in computer vision can be measured in a variety of ways, such as precision and recall, or more aggregate metrics like mean average precision (mAP). Picking the right metric is problem specific and usually comes down to which type of failure is the most important: false positives or false negatives.

@@

Package detection

\begin{itemize}
	\item Background material and texture.
	\item Lighting intensity and positioning.
	\item Object material and texture.
	\item Number of objects in view.
\end{itemize}

@@

Effect of domain randomized lighting

Effect of domain randomized backgrounds

>>>>

\author{
	{\hspace{1mm}Hugo Ponte}\footnote{Correspondence author} \\ 
	Zumo Labs \\
	\texttt{hugo@zumolabs.ai} \\
	\And
	{\hspace{1mm}Norman Ponte} \\
	Zumo Labs \\
	\texttt{norman@zumolabs.ai} \\
	\And
	{\hspace{1mm}Sammie Crowder} \\
	Zumo Labs \\
	\texttt{sammie@zumolabs.ai} \\
	\And
	{\hspace{1mm}Kory Stiger} \\
	Zumo Labs \\
	\texttt{kory@zumolabs.ai} \\
	\And
	{\hspace{1mm}Steven Pecht} \\
	Zumo Labs \\
	\texttt{steven@zumolabs.ai} \\
	\And
	{\hspace{1mm}Michael Stewart} \\
	Zumo Labs \\
	\texttt{michael@zumolabs.ai} \\
	\And
	{\hspace{1mm}Elena Ponte} \\
	Zumo Labs \\
	\texttt{elena@zumolabs.ai} \\
}

@@

Deep learning has exploded in popularity due to large open source frameworks such as tensorflow and pytorch

What is synthetic data.

@@

For a thorough review of synthetic data literature, we recommend readers go through Nikolenko's 2019 summary paper \citep{nikolenko2019synthetic}.

@@

In addition to supporting the full breadth of the 3D workflow, Blender has the unique strength of using Python as the programming language of choice for asset scripting. Python has emerged as the lingua franca for modern deep learning, in part due to the popularity of open-source frameworks such as TensorFlow \citep{tensorflow}, PyTorch \citep{pytorch}, and Scikit-Learn \citep{scikit-learn}. Successful adoption of synthetic data will require Machine Learning Engineers to perform asset scripting, and these engineers will be much more comfortable in Blender’s Python environment than Unity's C\# environment or Unreal Engine’s C++ tools.

@@

In this section we outline the key features and components of the zpy synthetic data toolkit.

@@

Blender allows for user-created AddOns, and provides tooling for integrating addon functionality with the Blender UI.

Popular AddOns include X, X, and X.

Those who use Blender in their 3D workflow are

@@

\subsection{Python Module}
\label{sec:python module}

@@

@@

@@

The first step in the syntehtic data workflow is to design and create the \emph{sim}, short for simulation. A sim is a collection of 3D assets controlled at runtime through a single script called the \emph{run script}. The run script defines a function \lstinline{run(**kwargs)}, which acts as the point of entry for any generation process. Important parameters that configure the behavior of the run script are defined as kwargs, short for keyword arguments, in the \lstinline{run(**kwargs)} function. These kwargs allow configuration of the simulation through gin-config, a python package for configuration of python libraries \citep{ginconfig}.

@@

\begin{lstlisting}[language=Python,caption={Basic structure of the run function in a sim run script.},label={lst:setuploop}]
def run(**kwargs):
	# Setup Code
	for frame in zpy.blender.step():
		# Loop Code
\end{lstlisting}

@@

Machine learning models are trained on a dataset for some time, and periodically evaluated on validation and test datasets. Model performance in computer vision can be measured in a variety of ways, such as precision and recall, or more aggregate metrics like mean average precision (mAP). Picking the right metric is problem specific and usually comes down to which type of failure is the most important: false positives or false negatives. It is important to note that though quantitative metrics are convenient, there is no replacement for qualitative analysis of model performance. We recommend that anyone building computer vision models take the time to examine model predictions on real images.

@@

To put into practice what this paper has explained, we present an example of how synthetic data can be used to train a computer vision model. In this example, we train a detection model which is tasked with predicting the bounding boxes for packages and parcels in images. In section \ref{sec:domainrandomization} we explore the effect of some key dataset hyperparameters on the final model performance. In section \ref{sec:curicculum} we discuss how training curriculum can affect model performance when using synthetic data.

Following the synthetic data workflow,

Armed with our synthetic training dataset and our real test dataset, we are ready to do some model training.

We used a ResNet model implemented in PyTorch inside of the Detectron2 computer vision library \citep{wu2019detectron2}.

@@

Domain randomization is a technique commonly used in synthetic data to increase the variance of a dataset distribution. In the field of synthetic data for computer vision, it might refer to randomizing the intensity of lighting in every frame of a simulation. Domain randomization is also important in the space of material assets: using a large variety of textures and material properties will help prevent texture overfitting, a common issue with CNNs \citep{DBLP:journals/corr/abs-1811-12231}.

In our package experiment, we expose two boolean toggles as run function kwargs that are categorized as forms of domain randomization. One toggle enables domain randomization in the lighting space: changing the position and intensity of several lights in the sim. The second toggle enables random HDRIs, which change the appearance of the background in the package images.
